### 2014-08-28 paper/paper.Rmd
revised intro

This paper will evaluate the role of several factors in which we see inequalities in mathematics, reading, and science outcomes. In section XXXgender, we will evaluate in what subjects we observe gender inequalities. In section XXX we will evaluate inequalities based on the household structure and occupation of the parents. In section XXXpossessions we will look at what home possessions are good predictors of inequalities. Lastly, in sections XXXschool, we will look at the role of school influences.

>>>>

The data was made available by the OECD as part of a data challenge for the useR! 2014 conference. Entries to the competition can be found at http://beta.icm.edu.pl/PISAcontest/. We learned a lot from this data, and won one of the prizes. This is a description of the seven main things we learned about 15 year olds, their math, science and reading skills, and the effects of other factors.
